---
title: "20201215 data project"
author: "mikiko"
date: "2020/12/15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
a
---

####  **Effects of landscape complexity and natural enemy exclusion on average daily aphid population growth across three sampling dates (1-3). **
APG: APhids population growth  
LC: Landscape complexity


```{r}
#import data file
library(readr)
Data1 <- read.table("Project data.csv", header = TRUE, dec = ",", sep =";")

###dataframe for sampling date1 
DATE1 <- Data1[Data1$Date == "1", ]
DATE1_700 <- subset(DATE1, DATE1$BUFF_DIST == "700")

```


####  **Bar graph**  
**Aphids population growth and Treatment**    
Effects of natural enemy exclusion on average daily aphid population growth across three sampling dates (1-3). 
Mean growth per exclusion treatment and sampling date.  


**Date1**   

```{r} 
#calculate the aphids population growth at date1
logNaphids_D1_bar <- log(DATE1$aphid_live+1) - log(DATE1$aphidsinoculated_init+1) 
APG_D1_bar <- logNaphids_D1_bar/10
#dataframe for seminatural habitat and aphids population growth at date1 
DATE1APG_bar <- data.frame(DATE1,APG_D1_bar)
```

```{r}
#plot
library(ggplot2)
Bar_APGD1 <- ggplot(DATE1APG_bar, aes(x = Treatment, y = APG_D1_bar, fill = Treatment))
Bar_APGD1 <- Bar_APGD1 + geom_bar(stat = "identity")
Bar_APGD1 <- Bar_APGD1 + labs(x= "Enemy exclution treatment", y="APhids population growth", title = "Effects of Treatment on APG at Date 1")
Bar_APGD1 <- Bar_APGD1 + geom_hline(yintercept=0, colour="grey") 
#Bar_APGD1 <- Bar_APGD1 + ylim(-0.1 , 0.15)
plot(Bar_APGD1)
```


**Date2**    
```{r}
####dataframe for sampling date2
DATE2 <- Data1[Data1$Date == "2", ]
DATE2_700 <- subset(DATE2, DATE2$BUFF_DIST == "700")

#Bar graph
#calculate the aphids population growth at date1
logNaphids_D2_bar <- log(DATE2$aphid_live+1) - log(DATE2$aphidsinoculated_init+1) 
APG_D2_bar <- logNaphids_D2_bar/20

#dataframe for seminatural habitat and aphids population growth at date1 
DATE2APG_bar <- data.frame(DATE2,APG_D2_bar)

#plot
Bar_APGD2 <- ggplot(DATE2APG_bar, aes(x = Treatment, y = APG_D2_bar, fill = Treatment))
Bar_APGD2 <- Bar_APGD2 + geom_bar(stat = "identity")
Bar_APGD2 <- Bar_APGD2 + labs(x= "Enemy exclution treatment", y="APhids population growth", title = "Effects of Treatment on APG at Date 2")
Bar_APGD2 <- Bar_APGD2 + geom_hline(yintercept=0, colour="grey") 
plot(Bar_APGD2)

```



**Date3**    
```{r}
####dataframe for sampling date3
DATE3 <- Data1[Data1$Date == "3", ]
DATE3_700 <- subset(DATE3, DATE3$BUFF_DIST == "700")

#calculate the aphids population growth at date1
logNaphids_D3_bar <- log(DATE3$aphid_live+1) - log(DATE3$aphidsinoculated_init+1) 
APG_D3_bar <- logNaphids_D3_bar/30

#dataframe for seminatural habitat and aphids population growth at date1 
DATE3APG_bar <- data.frame(DATE3,APG_D3_bar)

#plot
Bar_APGD3 <- ggplot(DATE3APG_bar, aes(x = Treatment, y = APG_D3_bar, fill = Treatment))
Bar_APGD3 <- Bar_APGD3 + geom_bar(stat = "identity")
Bar_APGD3 <- Bar_APGD3 + labs(x= "Enemy exclution treatment", y="APhids population growth", title = "Effects of Treatment on APG at Date 3")
Bar_APGD3 <- Bar_APGD3 + geom_hline(yintercept=0, colour="grey") 
plot(Bar_APGD3)


```






####  **Line graph**  
Effects of landscape complexity and natural enemy exclusion on average daily aphid population growth across three sampling dates (1-3).  
Variation of predicted values across the gradient in landscape complexity, measured by percent seminatural habitat in a 700 m radius around fields.  

**Date 1**  

```{r}
#calculate the aphids population growth at date1  
logNaphids_D1_line <- log(DATE1_700$aphid_live+1) - log(DATE1_700$aphidsinoculated_init+1) 
APG_D1_line <- logNaphids_D1_line/10 
```

```{r}
#dataframe for seminatural habitat and aphids population growth at date1   
DATE1APG_line <- data.frame(DATE1_700,APG_D1_line)  
```

```{r}
#barplot for % Seminatural habitat and APhid population growth
Line_APGD1 <- ggplot(DATE1APG_line, aes(x = Pt.seminatural, y = APG_D1_line, color = Treatment))
Line_APGD1 <- Line_APGD1 + labs(x= "% seminatural habitat", y="Aphids population growth", title = "Effects of Treatment on LC and APG at Date 1")
Line_APGD1 <- Line_APGD1 + geom_smooth(method = "lm")
Line_APGD1 <- Line_APGD1 +xlim(5,45) +ylim(-0.2 , 0.2)
print(Line_APGD1)
```


**Date2**    
```{r}
#calculate the aphids population growth at date1
logNaphids_D2_line <- log(DATE2_700$aphid_live+1) - log(DATE2_700$aphidsinoculated_init+1) 
APG_D2_line <- logNaphids_D2_line/20

#dataframe for seminatural habitat and aphids population growth at date1 
DATE2APG_line <- data.frame(DATE2_700,APG_D2_line)

#barplot for % Seminatural habitat and APhid population growth
Line_APGD2 <- ggplot(DATE2APG_line, aes(x = Pt.seminatural, y = APG_D2_line, color = Treatment))
Line_APGD2 <- Line_APGD2 + labs(x= "% seminatural habitat", y="Aphids population growth", title = "Effects of Treatment on LC and APG at Date 2")
# for scatter plot: use geom_point()
Line_APGD2 <- Line_APGD2 + geom_smooth(method = "lm")
Line_APGD2 <- Line_APGD2 +xlim(5,45) +ylim(-0.2 , 0.2)
print(Line_APGD2)
```


**Date3**    
```{r}
#calculate the aphids population growth at date1
logNaphids_D3_line <- log(DATE3_700$aphid_live+1) - log(DATE3_700$aphidsinoculated_init+1) 
APG_D3_line <- logNaphids_D3_line/30

#dataframe for seminatural habitat and aphids population growth at date1 
DATE3APG_line <- data.frame(DATE3_700,APG_D3_line)

#barplot for % Seminatural habitat and APhid population growth
Line_APGD3 <- ggplot(DATE3APG_line, aes(x = Pt.seminatural, y = APG_D3_line, color = Treatment))
Line_APGD3 <- Line_APGD3 + labs(x= "% seminatural habitat", y="Aphids population growth", title = "Effects of Treatment on LC and APG at Date 3")
# for scatter plot: use geom_point()
Line_APGD3 <- Line_APGD3 + geom_smooth(method = "lm")
Line_APGD3 <- Line_APGD3 +xlim(5,45) +ylim(-0.2 , 0.2)
print(Line_APGD3)

```



####  **Effects of landscape complexity and natural enemy exclusion on aphid parasitism rate at three sampling dates (dates 1–3; 10 day intervals).**

####  **Bar graph**   
Mean values per exclusion treatment and sampling date.


**Date1**  
```{r}
#dataframe for sampling date1 
DATE1 <- Data1[Data1$Date == "1", ]
DATE1_200 <-  subset(DATE1, DATE1$BUFF_DIST == "200")

# parasitism rate 
PR_D1_bar　<- DATE1$aphid_parasitized/(DATE1$aphid_live + DATE1$aphid_parasitized)

#add parasitism rate to the dataframe 
DATE1PR_bar <- data.frame(DATE1,PR_D1_bar)

#plot
Bar_PRD1 <- ggplot(DATE1PR_bar, aes(x = Treatment, y = PR_D1_bar, fill = Treatment))
Bar_PRD1 <- Bar_PRD1 + geom_bar(stat = "identity")
Bar_PRD1 <- Bar_PRD1 + labs(x= "Enemy exclution treatment", y="Parasitism rate", title = "Effects of Treatment on PR at Date 1")
plot(Bar_PRD1)

```


**Date2**  
```{r}
# parasitism rate 
PR_D2_bar　<- DATE2$aphid_parasitized/(DATE2$aphid_live + DATE2$aphid_parasitized)

#dataframe including PR
DATE2PR_bar <- data.frame(DATE2,PR_D2_bar)

#plot
Bar_PRD2 <- ggplot(DATE2PR_bar, aes(x = Treatment, y = PR_D2_bar, fill = Treatment))
Bar_PRD2 <- Bar_PRD2 + geom_bar(stat = "identity")
Bar_PRD2 <- Bar_PRD2 + labs(x= "Enemy exclution treatment", y="Parasitism rate", title = "Effects of Treatment on PR at Date 2")
plot(Bar_PRD2)

```


**Date3**  
```{r}
# parasitism rate - Treatment
PR_D3_bar　<- DATE3$aphid_parasitized/(DATE3$aphid_live + DATE3$aphid_parasitized)

#dataframe including parasitism rate at date3 
DATE3PR_bar <- data.frame(DATE3,PR_D3_bar)

#plot 
Bar_PRD3 <- ggplot(DATE3PR_bar, aes(x = Treatment, y = PR_D3_bar, fill = Treatment))
Bar_PRD3 <- Bar_PRD3 + geom_bar(stat = "identity")
Bar_PRD3 <- Bar_PRD3 + labs(x= "Enemy exclution treatment", y="Parasitism rate", title = "Effects of Treatment on PR at Date 3")
plot(Bar_PRD3)

```


####  **Effects of landscape complexity and natural enemy exclusion on syrphid fraction at three sampling dates (dates 1–3; 10 day intervals).**  


**Date1**  
```{r}
Data1 <- read.table("Project data.csv", header = TRUE, dec = ",", sep =";")
Date_1 <- Data1[Data1$Date == "1", ]
syrphid_fraction <- (Date_1$syrphidl_p /((Date_1$aphid_live)+(Date_1$syrphidl_p)))
Date_1$syrphid_fraction <- syrphid_fraction

Date1buff <- subset(Date_1, BUFF_DIST ==900)

# lm using Date_1
lm1 <- lm(Date1buff$syrphid_fraction ~ Date1buff$Pt.seminatural)
plot(Date1buff$syrphid_fraction ~ Date1buff$Pt.seminatural)

# ggplot using Date1buff
ggplot(Date1buff, aes(x= Pt.seminatural, y= syrphid_fraction, 
                   color = Treatment)) +
  geom_jitter()+
  geom_smooth(method="exp")

#barplot using Date_1
G1 <- ggplot(Date_1, aes(x= Treatment, y= syrphid_fraction, fill = Treatment))+
  geom_bar(stat="identity")+
  labs(x="Treatment", y="Syrphid fraction", title="Effect of NE treatment on syrphid fraction at Date 1")

```


**Date2**   
```{r}
# lm using Date_2
Date_2 <- Data1[Data1$Date == "2", ]
syrphid_fraction <- (Date_2$syrphidl_p /((Date_2$aphid_live)+(Date_2$syrphidl_p)))
Date_2$syrphid_fraction <- syrphid_fraction

Date2buff <- subset(Date_2, BUFF_DIST ==900)

lm1 <- lm(Date_2$syrphid_fraction ~ Date_2$Pt.seminatural)
plot(Date_2$syrphid_fraction ~ Date_2$Pt.seminatural)

# ggplot using Date2buff
ggplot(Date2buff, aes(x= Pt.seminatural, y= syrphid_fraction, 
                      color = Treatment)) +
  geom_jitter()+
  geom_smooth(method="exp")

#barplot using Date_2
G1 <- ggplot(Date_2, aes(x= Treatment, y= syrphid_fraction, fill = Treatment))+
  geom_bar(stat="identity")+
  labs(x="Treatment", y="Syrphid fraction", title="Effect of NE treatment on syrphid fraction at Date 2")
print(G1)

```




**Date3**   
```{r}
Date_3 <- Data1[Data1$Date == "3", ]
syrphid_fraction <- (Date_3$syrphidl_p /((Date_3$aphid_live)+(Date_3$syrphidl_p)))
Date_3$syrphid_fraction <- syrphid_fraction

Date3buff <- subset(Date_3, BUFF_DIST ==900)


# lm using Date_3
lm1 <- lm(Date_3$syrphid_fraction ~ Date_3$Pt.seminatural)
plot(Date_3$syrphid_fraction ~ Date_3$Pt.seminatural)

# ggplot using Date3buff
ggplot(Date3buff, aes(x= Pt.seminatural, y= syrphid_fraction, 
                      color = Treatment)) +
  geom_jitter()+
  geom_smooth(method="exp")

#barplot using Date_3
G1 <- ggplot(Date_3, aes(x= Treatment, y= syrphid_fraction, fill = Treatment))+
  geom_bar(stat="identity")+
  labs(x="Treatment", y="Syrphid fraction", title="Effect of NE treatment on syrphid fraction at Date 3")
print(G1)

# one inconsistency: second highest number should not be HPGD, but HGD according to the article. 

```




